### 2017-10-31 manuscript.rmd
included bracts 1/0 in tip annotation overview figure 4a

@@

#####Overview grid of main binary traits
```{r ggtree_bin_heatmap, echo=F, message=F, warning=F}
p <- ggtree(ultratree)
p <- p + geom_tiplab(size=3)
f_cdata = sapply(cdata, as.factor) %>% as.data.frame %>% .[c(2,5:7)]
rownames(f_cdata) = rownames(cdata)
names(f_cdata)[4] = "Float"
gheatmap(p, f_cdata, offset = 0.4, width=0.5, colnames_position = 'top', font.size = 3)
```

>>>>

bracts = cdata$Bract.types
bracts[which(bracts>0)] <- 1  #bracts changed to presence absence for tip annotation
names(bracts) = rownames(cdata)
cdata$Bract.types = bracts
names(cdata)[8] = "Bracts"

@@

####Overview grid of main binary traits
```{r ggtree_bin_heatmap, echo=F, message=F, warning=F}
p <- ggtree(ultratree)
p <- p + geom_tiplab(size=3)
f_cdata = sapply(cdata, as.factor) %>% as.data.frame %>% .[c(2,5:8)]
rownames(f_cdata) = rownames(cdata)
names(f_cdata)[4] = "Float"
gheatmap(p, f_cdata, offset = 0.4, width=0.5, colnames_position = 'top', font.size = 1.6)
```
